BACI of biomass change for VOCC source cells

### 2019-08-20 analysis/VOCC/4-vocc-BACI.Rmd
automate changing variables

#### Set vector type
```{r echo=TRUE}
 climate <- "temperature"
# climate <- "do"
# climate <- "do and temperature"
```

@@

Prep data
```{r}
data <- vocc_by_sp[["adult"]]
#View(data)
data$log_density <-  log(data$density)
data$distance2 <- data$distance^2

@@

Plot data
```{r}
ggplot(data, aes(y=log_density, x=temp, colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C")

@@

Basic BACI
```{r}

m <- lmerTest::lmer(log_density~after + cell_type + after:cell_type + std_temp + std_temp2 + distance + distance2 + (1|icell) + (1|matchobs), data=data)
summary(m)
```

@@

GAMM
```{r}
gam4 <- gamm4::gamm4(log_density~ time * cell_type + s(std_temp) + s(distance) + s(X,Y), 
  random = ~(1|matchobs) + (1|origobs), data=data) # + s(X,Y, bs="re")

@@

Plot data
```{r}
ggplot(idata, aes(y=log_density, x=temp, colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C")

ggplot(idata, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)

@@

Basic BACI
```{r}
mi <- lmerTest::lmer(log_density ~ as.factor(after) + cell_type + after:cell_type + std_temp + std_temp2 + distance + distance2 + (1|icell) + (1|matchobs), data=idata)
summary(mi)
```

@@

GAMM
```{r}
igam4 <- gamm4::gamm4(log_density~ time * cell_type + s(std_temp) + s(distance) + s(X,Y), 
  random = ~(1|matchobs) + (1|origobs), data=idata) # + s(X,Y, bs="re")

>>>>

#### Set vector type
```{r echo=TRUE}
# climate <- "temperature"
 climate <- "do"
# climate <- "do and temperature"
```

@@

Prep data
```{r}
data <- vocc_by_sp[["adult"]]
#View(data)

data$log_density <-  log(data$density)
data$distance2 <- data$distance^2

@@

Plot data
```{r}
lapply(variable_names, function(j) {
ggplot(data, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") 
})

@@

Basic BACI
```{r}
for (j in (variable_names)) {
  baci_formula <- paste0("log_density~after + cell_type + after:cell_type + distance + distance2 + std_", j, "+ std_", j, "2 + (1|icell) + (1|matchobs)")
}

m <- lmerTest::lmer(as.formula(baci_formula), data=data)
summary(m)
```

@@

GAMM
```{r}

for (j in (variable_names)) {
  gamm_formula <- paste0("log_density ~ time * cell_type + s(distance) + s(std_", j, ") + s(X,Y)")
}

gam4 <- gamm4::gamm4(as.formula(gamm_formula),random = ~(1|matchobs) + (1|origobs), data=data) # + s(X,Y, bs="re")

@@

Plot data
```{r}
lapply(variable_names, function(j) {
ggplot(idata, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") 
})
ggplot(idata, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)

@@

Basic BACI
```{r}
mi <- lmerTest::lmer(as.formula(baci_formula), data=idata)
summary(mi)
```

@@

GAMM
```{r}
# for (j in (variable_names)) {
#   gamm_formula <- paste0("log_density ~ time * cell_type + s(distance) + s(std_", j, ") + s(X,Y)")
# }

igam4 <- gamm4::gamm4(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs), data=idata) # + s(X,Y, bs="re")
